Polyglots: Crossing Origins by Crossing Formats

### 2013-08-25 main.tex
Minor edit
Fixed some todos, still missing images.

\documentclass{sig-alternate}
%\documentclass[10pt, conference, compsocconf]{IEEEtran}
%\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{epsfig,endnotes}

@@

\makeatletter
\def\@maketitle{\newpage
 \null
 \setbox\@acmtitlebox\vbox{%
\baselineskip 20pt
%\vskip 2em                   % Vertical space above title.
%\vskip 0em                   % Vertical space above title.
   \begin{center}
    {\ttlfnt \@title\par}       % Title set in 18pt Helvetica (Arial) bold size.
%    \vskip 1.5em                % Vertical space after title.
%This should be the subtitle.
{\subttlfnt \the\subtitletext\par}\vskip 1.25em%\fi
    {\baselineskip 16pt\aufnt   % each author set in \12 pt Arial, in a
     \lineskip .5em             % tabular environment
     \begin{tabular}[t]{c}\@author
     \end{tabular}\par}
 %   \vskip 1.5em               % Vertical space after author.
   \end{center}}
 \dimen0=\ht\@acmtitlebox
% \advance\dimen0 by -12.75pc\relax % comment by Marco Daniel
 \unvbox\@acmtitlebox
 \ifdim\dimen0<0.0pt\relax\vskip-\dimen0\fi}
\makeatother

@@

%\author{}
% \author{\IEEEauthorblockN{Jonas Magazinius} 
% \IEEEauthorblockA{Department ofComputer Science\\ 
% Chalmers University of Technology\\ 
% Gothenburg, Sweden\\
% jonas.magazinius@chalmers.se} 
% \and 
% \IEEEauthorblockN{Billy Rios} 
% \IEEEauthorblockA{dept. name of organization\\ 
% name of organization, acronyms acceptable\\ 
% City, United States of America\\ 
% Email: name@xyz.com} 
% \and 
% \IEEEauthorblockN{Andrei Sabelfeld} 
% \IEEEauthorblockA{Department of Computer Science\\ 
% Chalmers University of Technology\\ 
% Gothenburg, Sweden\\ 
% andrei@chalmers.se} 
% }

@@

% \begin{IEEEkeywords}
% Web Security; Polyglot; Injection; Cross-domain.
% \end{IEEEkeywords}

@@

\paragraph{Crossing origins by crossing formats}
This paper identifies a new breed of attacks and its root cause:
\emph{polyglots}. 
%
A polyglot is a program that is valid in multiple programming languages.
%
In a heterogeneous system like the web, information is exchanged
between components in versatile formats.
%
This gives rise to attacks that exploit the mismatch between the
expected and provided content.
%
Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.
An attacker can use a polyglot to infiltrate a vulnerable origin.
Once infiltrated, the polyglot is embedded from within the attacker's web site,
so that the polyglot is loaded in the browser's plug-in.
According to the SOP, content loaded in a plug-in is considered to belong to the 
origin from which the content was requested, thus allowing the polyglot to communicate with the vulnerable 
origin. A victim visiting the attacker's web site, while authenticated in the vulnerable
origin, will activate the malicious polyglot, which can abuse the credentials of the victim 
in its communication with the vulnerable service. The scenario is explained in detail in Section~\ref{sec:vectors},
where we present novel attack vectors that are based on (i)
\emph{syntax injection} that 
operate across multiple languages and on (ii) \emph{content smuggling} that supply
malicious payload that appears formatted as benign content. The
attacks lead to both \emph{cross-domain leakage} and \emph{cross-site
request forgery}.

@@

By crossing origins we mean being able to request and access content
which is normally restricted under the same-origin policy. 
Recall that SOP only allows two documents accessing each others'
content and resources if they share the origin.
%\todo{More on SOP}
Similarly,
a document can only directly communicate with the server from which it originates. 
This is not to be confused with \emph{cross-origin resource sharing} (CORS)~\cite{w3-cors}, which is an 
intentional relaxation of SOP.

@@

Not all elements are as carefully restricted from information leaks as images. 
Scripts loaded across origins become part of the document and inherit the 
origin of the including document, which allows the script to communicate with the 
server from which the \emph{document} originates. Such scripts are also able to interact 
with the document, e.g. by adding nodes, which in turn require new content to be 
requested. Since these requests are not restricted by SOP, this creates a side 
channel that permits cross-origin information leakage. At the same time, the including document
is prevented from inspecting the source of the script and can only observe the public 
side-effects that the script produce as it is executed.

@@

A polyglot is composed from various constructs that are either common between
languages; or constructs that are language specific but carrying different
meaning in each language. To maintain validity across languages, one must ensure
that language specific constructs are not interpreted by other languages. This
is often accomplished by hiding the parts of the code specific to one language,
in parts interpreted as comments or plain text of another.

Certain languages are particularly suitable for creating polyglots. These
languages either have a lot of constructs in common with other languages, such
as the C language, or are defined such that the parser ignores that which it cannot
interpret, such as HTML. The latter allows for ample opportunity to hide
any code specific to another language, as long as there is no overlap with the
syntax of the first language.

@@

A malicious polyglot is composed of two formats where one is benign in nature and the other
contains a malicious payload. 
% Characteristics of a malicious polyglot
The benign format is a widely accepted format with the capability 
of hiding arbitrary data, e.g. an image with comment fields. The malicious 
format has additional capabilities, such as scripting.
% Under what circumstances can a polyglot be malicious
This kind of polyglot can be used for malicious purposes when there is a difference between
the expected run-time context and the actual context it is executed in. 
In the expected context the content is interpreted as the 
benign format. In the actual context, however, the content is coerced to be 
interpreted as the malicious format containing the payload.

Even if a verification process exists, it verifies that the content is valid 
in the expected context. Due to the nature of the polyglot, the content is 
verified as valid and benign, but subsequently the malicious
content is executed.

Coercing content to be interpreted
as a different type can be accommodated in the context of the web. 
If the content is loaded using an \emph{image} tag it will be interpreted 
as an image, if a \emph{script} tag is used it will be interpreted as a script. Some 
tags even let the developer decide which type to interpret the content as. 
To prevent abuse, the browsers employ content-type 
sniffing for certain content-types, a practice which has historically led to 
security issues. 
%

@@

While these articles document known instances of polyglot attacks, the attack 
method has not been generalized until this paper.
%
Under our generalization, previous work corresponds to
instances. For example, we show that GIFAR attacks describe a form of content smuggling, and
cross-origin CSS attacks describe a form of syntax injection attacks.
%
The added value of our paper is a generalized view and focus on new
instances of polyglots that involve the PDF format.

@@

Previous work documents an instance of a polyglot attack based on syntax injection, though not phrased in those terms.
Huang et al.~\cite{Huang+:CCS10} describe a cross-origin \emph{cascading style-sheet} (CSS) attack. This 
attack injects fragments of CSS syntax in a HTML 
document, thereby making it a HTML/CSS polyglot. The error-tolerant parsing of 
style sheets allow the polyglot to parsed as valid CSS. The capabilities of CSS 
provide trivial cross-origin leakage. The paper proposes a defense technique which has been
adopted by all major browsers, which implies that the attacks outlined in their paper are now ineffective.
Instead,
Section
\ref{sec:vuln} will show practical attacks based on other formats.

@@

To prevent PDF-based syntax injection attack, the task is simpler. As discussed in Section~\ref{sec:pdf-injection}, the token-set identified in 
Section~\ref{sec:pdf-injection}, are essential 
to create valid PDF syntax. %, namely \emph{'$<$', '$>$', and '/'}.
Filtering 
user input to remove or encode these characters effectively mitigates the 
vulnerability. 
Luckily, because of the significant overlap with the token-set
of HTML, many of the contexts where user input can occur are already being protected.
Special attention is required in contexts are not traditionally filtered for 
HTML tokens, e.g. JSON.

>>>>

\documentclass{sig-alternate-2013}
%\documentclass[10pt, conference, compsocconf]{IEEEtran}
%\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{epsfig,endnotes}

%%%%%%%%%%%%%%%%
% ACM Copyright text
% Check if this is the correct version
%%%%%%%%%%%%%%%%
\newfont{\mycrnotice}{ptmr8t at 7pt}
\newfont{\myconfname}{ptmri8t at 7pt}
\let\crnotice\mycrnotice%
\let\confname\myconfname%

\permission{Permission to make digital or hard copies of all or part of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than ACM must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from permissions@acm.org.}
\conferenceinfo{CCS'13,}{November 4--8, 2013, Berlin, Germany.}
\copyrightetc{Copyright 2013 ACM \the\acmcopyr}
\crdata{978-1-4503-2477-9/13/11\ ...\$15.00.\\
http://--enter the whole DOI string from rightsreview form confirmation}

\clubpenalty=10000 
\widowpenalty = 10000

@@

%\makeatletter
%\def\@maketitle{\newpage
% \null
% \setbox\@acmtitlebox\vbox{%
%\baselineskip 20pt
%%\vskip 2em                   % Vertical space above title.
%%\vskip 0em                   % Vertical space above title.
%   \begin{center}
%    {\ttlfnt \@title\par}       % Title set in 18pt Helvetica (Arial) bold size.
%%    \vskip 1.5em                % Vertical space after title.
%%This should be the subtitle.
%{\subttlfnt \the\subtitletext\par}\vskip 1.25em%\fi
%    {\baselineskip 16pt\aufnt   % each author set in \12 pt Arial, in a
%     \lineskip .5em             % tabular environment
%     \begin{tabular}[t]{c}\@author
%     \end{tabular}\par}
% %   \vskip 1.5em               % Vertical space after author.
%   \end{center}}
% \dimen0=\ht\@acmtitlebox
%% \advance\dimen0 by -12.75pc\relax % comment by Marco Daniel
% \unvbox\@acmtitlebox
% \ifdim\dimen0<0.0pt\relax\vskip-\dimen0\fi}
%\makeatother

@@

\numberofauthors{3}
\author{\alignauthor
Jonas Magazinius\\
\affaddr{Department of Computer Science}\\
\affaddr{Chalmers University of Technology}\\
\affaddr{Gothenburg, Sweden}\\
\email{jonas.magazinius@chalmers.se}
\alignauthor 
Billy K. Rios\\
\affaddr{Cylance, Inc.}\\ 
\affaddr{Irvine, United States of America}\\ 
\email{billy.rios@gmail.com} 
\alignauthor
Andrei Sabelfeld\\
\affaddr{Department of Computer Science}\\ 
\affaddr{Chalmers University of Technology}\\ 
\affaddr{Gothenburg, Sweden}\\ 
\email{andrei@chalmers.se} 
}

@@

\category{H.4}{Information Systems Applications}{Miscellaneous}

\keywords{Web Security, Polyglot, Injection, Cross-domain}

@@

\paragraph{Crossing origins by crossing formats}
This paper identifies a new breed of attacks and its root cause:
\emph{polyglots}. 
%
A polyglot is a program that is valid in multiple programming languages.
%
In a heterogeneous system like the web, information is exchanged
between components in versatile formats.
%
This gives rise to attacks that exploit the mismatch between the
expected and provided content.
%
Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.
An attacker can use a malicious polyglot to infiltrate a vulnerable origin.
Once infiltrated, the polyglot is embedded from within the attacker's web site,
such that the browser is coerced to interpret the polyglot in an unexpected context, e.g., a plug-in.
According to the SOP, content loaded in a plug-in is considered to belong to the 
origin from which the content was requested. Thus, the polyglot is allowed to communicate with the vulnerable 
origin. A victim, authenticated in the vulnerable origin, who visits the attacker's web site
will trigger the malicious polyglot. This allows the polyglot to abuse the credentials of the victim 
in its communication with the vulnerable service. The scenario is explained in detail in Section~\ref{sec:vectors},
where we present novel attack vectors that are based on (i)
\emph{syntax injection} that 
operate across multiple languages and on (ii) \emph{content smuggling} that supply
malicious payload that appears formatted as benign content. The
attacks lead to both \emph{cross-domain leakage} and \emph{cross-site
request forgery}.

@@

By crossing origins we mean being able to request and access content
across domains, which is normally restricted under the same-origin policy. 
Recall that SOP only allows two documents accessing each others'
content and resources if they share the origin.
%\todo{More on SOP}
Similarly,
a document can only directly communicate with the server from which it originates. 
This is not to be confused with \emph{cross-origin resource sharing} (CORS)~\cite{w3-cors}, which is an 
intentional relaxation of SOP.

@@

Not all elements are as carefully restricted from information leaks as images. 
Scripts loaded across origins become part of the document and inherit the 
origin of the including document, which allows the script to communicate with the 
server from which the \emph{document} originates. Such scripts are also able to interact 
with the document, e.g. by adding nodes, which in turn require new content to be 
requested. Since these requests are not restricted by the SOP, this creates a side 
channel that permits cross-origin information leakage. At the same time, the including document
is prevented from inspecting the source of the script and can only observe the public 
side-effects that the script produce as it is executed.

@@

A polyglot is composed by combining syntax from two different formats A and B. 
It leverages various syntactic language constructs that are either common between
the formats; or constructs that are language specific but carrying different
meaning in each language. To maintain validity across languages, one must ensure
that constructs specific to A are not interpreted in the format of B, and vice versa. This
is often accomplished by hiding the language specific constructs,
in segments interpreted as comments or plain text of the other format.

Certain languages are particularly suitable for creating polyglots. These
languages either have a lot of constructs in common with other languages, such
as the C language, or are error tolerant in that the parser ignores that which it cannot
interpret, such as HTML. The latter allows for ample opportunity to hide
any code specific to format A, as long as there is no overlap with the
syntax of format B.

@@

A malicious polyglot of two formats, \emph{A} and \emph{B}, where \emph{A} is benign in 
nature and \emph{B} contains a malicious payload, is composed as \emph{A||B}. 
% Characteristics of a malicious polyglot
he benign format, \emph{A}, is a widely accepted format with limited capabilities,
but with the opportunity of hiding arbitrary data, e.g. an image with comment fields. The malicious 
format, \emph{B}, has additional capabilities, e.g., execute scripts or send requests.
% Under what circumstances can a polyglot be malicious
This kind of polyglot can be used for malicious purposes when there is a difference between
the assumed run-time context, and the actual context it is executed in. 
In the assumed context \emph{A||B}  is interpreted as the 
benign format, \emph{A}. In the actual context, however, \emph{A||B} is coerced to be 
interpreted as the malicious format, \emph{B}, containing the payload.

Even if a verification process exists, it will verify that the content is valid 
in the assumed context. Due to the nature of the polyglot, the content is 
verified as valid and benign, but subsequently, in the actual context, the malicious
content is executed.

Coercing content to be interpreted
as a different type can be accommodated in the context of the web. 
If the content is loaded using an \emph{image} tag it will be interpreted 
as an image, if a \emph{script} tag is used it will be interpreted as a script. Certain
tags, e.g., the object-tag and embed-tag, even let the developer decide which type to interpret the content as. 
To prevent abuse, the browsers employ content-type 
sniffing for certain content-types, a practice which has historically led to 
security issues. 
%

@@

While these articles document known instances of polyglot attacks, the attack 
method has not been generalized until this paper.
%
Under our generalization, previous work corresponds to
instances. For example, we show that GIFAR attacks describe a form of content smuggling, Section~\ref{sec:smuggling}, and
cross-origin CSS attacks~\cite{Huang+:CCS10} describe a form of syntax injection attacks, Section~\ref{sec:injection}.
%
The added value of our paper is a generalized view and focus on new
instances of polyglots that involve the PDF format.

@@

Previous work documents an instance of a polyglot attack based on syntax injection, though not phrased in those terms.
Huang et al.~\cite{Huang+:CCS10} describe a cross-origin \emph{cascading style-sheet} (CSS) attack. This 
attack injects fragments of CSS syntax in a HTML 
document, thereby making it a HTML/CSS polyglot. The error-tolerant parsing of 
style sheets allow the polyglot to parsed as valid CSS. The capabilities of CSS 
provide trivial cross-origin leakage. The paper proposes a defense technique which has been
adopted by all major browsers, which implies that the attacks outlined in their paper are now ineffective.
Instead,
Section~\ref{sec:vuln} will show practical attacks based on other formats.

@@

To prevent attacks based on a specific format, e.g., a PDF-based syntax injection attack, the task is simpler. As discussed in Section~\ref{sec:pdf-injection}, the token-set identified in 
Section~\ref{sec:pdf-injection}, are essential 
to create valid PDF syntax. %, namely \emph{'$<$', '$>$', and '/'}.
Filtering 
user input to remove or encode these characters effectively mitigates the 
vulnerability. 
Luckily, because of the significant overlap with the token-set
of HTML, many of the contexts where user input can occur are already being protected.
Special attention is required in contexts are not traditionally filtered for 
HTML tokens, e.g. JSON.
